Verifying Demonstrations

### 2018-02-06 paper/NIZK-anon-cred.tex
Updates bibsp, clarifies intro to NIZK-anon-cred

\subsection{Non-interactive anonymous credentials}%
\label{NIZK-proofs}

\NewScheme{\Psig}{Psig}

\Citet{Psignatures} proposes P-signatures (\Psig), which provides a signature 
scheme and a commitment scheme with a protocol to obtain a signature on a 
committed value and two non-interactive proof systems, one for proving that a 
committed value has been signed and the other for proving that a pair of 
commitments are commitments to the same value.

\NewFunction{\PSetup}{\Psig.\!Setup}

@@

\NewFunction{\PCommit}{\Psig.\!Commit}

@@

\NewFunction{\PObtainSig}{\Psig.\!ObtainSig}
\NewFunction{\PIssueSig}{\Psig.\!IssueSig}

@@

\NewFunction{\PProve}{\Psig.\!Prove}

@@

\NewFunction{\PVerifyProof}{\Psig.\!VerifyProof}

@@

\NewFunction{\PEqCommProve}{\Psig.\!EqCommProve}

@@

\NewFunction{\PVerEqComm}{\Psig.\!VerEqComm}

>>>>

\subsection{Non-interactive anonymous credentials}%
\label{NIZK-anon-cred}

\NewCryptoScheme{\Psig}{Psig}

\Citet{Psignatures} presents a class of signatures, commitments and 
non-interactive proof protocols named P-signatures (\Psig), which yields for 
creating non-interactive anonymous credentials.
P-signatures provides a signature scheme and a commitment scheme with a protocol 
to obtain a signature on a committed value and two non-interactive proof 
systems, one for proving that a committed value has been signed and the other 
for proving that a pair of commitments are commitments to the same value.

\NewCryptoFunction{\PSetup}{\Psig.\!Setup}

@@

\NewCryptoFunction{\PCommit}{\Psig.\!Commit}

@@

\NewCryptoFunction{\PObtainSig}{\Psig.\!ObtainSig}
\NewCryptoFunction{\PIssueSig}{\Psig.\!IssueSig}

@@

\NewCryptoFunction{\PProve}{\Psig.\!Prove}

@@

\NewCryptoFunction{\PVerifyProof}{\Psig.\!VerifyProof}

@@

\NewCryptoFunction{\PEqCommProve}{\Psig.\!EqCommProve}

@@

\NewCryptoFunction{\PVerEqComm}{\Psig.\!VerEqComm}
